New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/schur.tex
exemple template

@@

The first inequality comes from the original Schur's paper \cite{Schur1917}. The second one are due to
Abott \cite{AbbottHanson}
and the third one to Rowley \cite{RowleyRamsey}. The other ones are new. \\

@@

>>>>

See below an example of such a construction. \\
It is quite similar to Abott and Hanson construction \cite{AbbottHanson}. They extend vertically a sum-free partition,
and horizontally an other sum-free partition. This way each "block" acts like a security zone for the other one.
Here, the horizontal partition is no longer to the side of the vertical one, but occupies the column of the special color
of the \(SF\)-template, i.e the one without the extra condition.

@@

The first inequality comes from the original Schur's paper \cite{Schur1917}. The second one is due to
Abott \cite{AbbottHanson}
and the third one to Rowley \cite{RowleyRamsey}. The other ones are new. \\

@@

\textsc{Proof :} The idea is the same as in the previous theorem. The only difference is the \(SF\) property inherited 
from the second \(SF\)-template.
